Supporting Information

### 2016-08-13 portfolio/text/supp.Rnw
Switch SI to .Rnw

@@

>>>>

<<set-knitr-options, cache=FALSE, echo=FALSE>>=
library("knitr")
opts_chunk$set(fig.align='center', fig.pos="htpb", cache=TRUE, echo=FALSE,
  message=FALSE, autodep=TRUE, results='hide', fig.path='../figs/',
  fig.width=6, par=TRUE)
opts_chunk$set(warning=FALSE, message=FALSE, tidy=FALSE, refresh=TRUE,
  cache.path="../cache/", cache.lazy=TRUE, size="small", cache.comments=FALSE)
opts_chunk$set(dev = 'pdf')
opts_knit$set(out.format = "latex", out.width="\\textwidth")
opts_knit$set(eval.after = 'fig.cap') # evaluate fig.cap after the chunk
opts_chunk$set(collapse = TRUE, comment = "")
@

<<get-values, cache=TRUE>>=
wd <- getwd()
setwd("../../")
source("portfolio/analysis/prep-stan-model-matrix.R")
rows_dat <- nrow(mm)
setwd(wd)
@

@@

Rows of data: \Sexpr{rows_dat}.
